Bayesian neural networks for sparse coding

### 2018-10-25 icassp_2019/paper.tex
update graphics in paper

   \begin{figure*}[!t]
  \centering
  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
  \label{fig:nmse_n_layers_synthetic}}
  \hfil
  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_undersampling/nmse_validation}
  \label{fig:nmse_undersampling_synthetic}}
  \hfil
  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/100_nmse_valid}
  \label{fig:nmse_k_100}}
  \hfil
  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/250_nmse_valid}
  \label{fig:nmse_k_250}}
  \caption{\textsc{nmse} results. The synthetic data for different number of layers (for NNs) or iterations (for \textsc{ista} and \textsc{fista}~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}. \textsc{mnist} data with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
  \label{fig:number_of_layers_synthetic}
  \end{figure*}

>>>>

   \begin{figure*}[!t]
  \centering
  \subfloat[Synthetic for different $L$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_number_of_layers/nmse_validation}
  \label{fig:nmse_n_layers_synthetic}}
  \hfil
  \subfloat[Synthetic for different $K$]{\includegraphics[width=0.24\textwidth]{graphics/synthetic_undersampling/nmse_validation}
  \label{fig:nmse_undersampling_synthetic}}
  \hfil
  \subfloat[\textsc{mnist} for $K = 100$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/100_nmse_valid}
  \label{fig:nmse_k_100}}
  \hfil
  \subfloat[\textsc{mnist} for $K = 250$]{\includegraphics[width=0.24\textwidth]{graphics/mnist/250_nmse_valid}
  \label{fig:nmse_k_250}}
  \caption{\textsc{nmse} results. The synthetic data for different number of layers~\protect\subref{fig:nmse_n_layers_synthetic} and for different sizes of observations~\protect\subref{fig:nmse_undersampling_synthetic}. \textsc{mnist} results for increasing number of iterations with the observation size $K = 100$~\protect\subref{fig:nmse_k_100} and $K = 250$~\protect\subref{fig:nmse_k_250}}
  \label{fig:number_of_layers_synthetic}
  \end{figure*}
